---
output:
  github_document:
    html_preview: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

`binomial` is a package that provides functions for bino mial distributions.

* `bin_choose()` calculates the number of combinations in which $k$ successes can occur in $n$ trials.

* `bin_probability()` calculates the probability in which $k$ successes can occur in $n$ trials with the probability of success.

* `bin_distribution()` calculates the binomial distribution with an output as a data frame with class `"bindis","data.frame"`.

* `plot()` method for a binomial distribution creates a barplot.

* `bin_cumulative()` calculates the cumulative probability of a binomial distribution. The output is a data frame with class `"bincum","data.frame"`.

* `plot()` function gives you a line plot of the cumulative distribution.

* `bin_variable()` gives the binomial variable with class `"binvar"`. It prints out the parameters.

* `summary()` functions gives you a summary of the variable: mean, variable, mode, skewness, kurtosis.

* `bin_mean()` calculates mean of binomial distributions.

* `bin_variance()` calculates variance of binomial.

* `bin_mode()` calculates mode of binomial distributions.

* `bin_skewness()` calculates skewness of binomial distributions.

* `bin_kurtosis()` calculates kurtosis of binomial distributions


## Motivation

This package has been developed for the model of binomial distribution.


## Usage

```{r}
library(binomial)

bin_choose(n = 5, k = 2)

# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5) 
bin_probability(success = 2, trials = 5, prob = 0.5)

bin_distribution(trials=5, prob = 0.5)

dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)

bin_cumulative(trials=5, prob = 0.5)

dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)

bin_variable(trials = 10, p = 0.3)

bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1

bin_mean(trials = 10, prob = 0.3)

bin_variance(trials = 10, prob = 0.3)

bin_mode(trials = 10, prob = 0.3)

bin_skewness(trials = 10, prob = 0.3)

bin_kurtosis(trials = 10, prob = 0.3)
```
