---
title: "Getting Started with binomial"
author: "Xinran Song"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Getting started with binomial

First, load the package.
```{r}
library(binomial)
```

Binomial distribution is the theoretical probability model we use when calculating probabilities about the number of successes in a fixed number of random trials performed under identical conditions (assuming a constant probability of success on each trial).


## Binomial choose

The first step is to calculates the number of combinations in which $k$ successes can occur in $n$ trials.

```{r}
bin_choose(n = 5, k = 2)
```

## Binomial Probability

Then, we can calculate the probability in which $k$ successes can occur in $n$ trials with the probability of success. In this process, the function takes three arguments: success, trials, and prob.

```{r}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5) 
bin_probability(success = 2, trials = 5, prob = 0.5)
```

## Binomial Distribution

When we calculate the binomial distribution, we get a data frame with class `"bindis","data.frame"`.

```{r}
bin_distribution(trials=5, prob = 0.5)
```

The `plot()` function gives you a barplot of the distribution:
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## Binomial Cumulative

`bin_cumulative()` calculates the cumulative probability of a binomial distribution. The output is a data frame with class `"bincum","data.frame"`.

```{r}
bin_cumulative(trials=5, prob = 0.5)
```

The `plot()` function gives you a line plot of the cumulative distribution:
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

## Binomial Variable

`bin_variable()` gives the binomial variable with class `"binvar"`. It prints out the parameters.

```{r}
bin_variable(trials = 10, p = 0.3)
```

The `summary()` functions gives you a summary of the variable: mean, variable, mode, skewness, kurtosis. It is printed out nicely:

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

## Measures

`bin_mean()` calculates mean of binomial distributions:
```{r}
bin_mean(trials = 10, prob = 0.3)
```

`bin_variance()` calculates variance of binomial distributions:
```{r}
bin_variance(trials = 10, prob = 0.3)
```

`bin_mode()` calculates mode of binomial distributions:
```{r}
bin_mode(trials = 10, prob = 0.3)
```

`bin_skewness()` calculates skewness of binomial distributions:
```{r}
bin_skewness(trials = 10, prob = 0.3)
```

`bin_kurtosis()` calculates kurtosis of binomial distributions:
```{r}
bin_kurtosis(trials = 10, prob = 0.3)
```

